---
title: "$I^2C$ Analysis"
author: "Nickolas Gallegos"
date: "2023-04-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This document will be used to analyze capture data from the $I^2C$ module for \newline
the _Wagner_ Project.


The data is exported from the Saleae Logic Analyzer application and stored in \newline
the "Captures" folder of the R Project.

# Data

The file is _i2c_2peripheral.csv_ and contains a logic capture of interactions \newline
between one controller device (Raspberry Pi Pico) and two peripheral devices \newline
(Adafruit ItsyBitsy and Adafruit Trinket M0).

## Read in Data

```{r}
file <- "../Captures/i2c_2peripheral.csv"
data1 <- read.csv(file)

#View(data1)

head(data1)
tail(data1)
colnames(data1)
```

## Clean Data and create subsets

The data has column names:  
  - name  
  - type  
  - start_time  
  - duration  
  - ack  
  - address  
  - read  
  - data  
  - description  
  - count  
  - action  
  
  
The important columns will be the _type_, _start_time_, _duration_, _address_, _read_, _data_

Get rid of the "I2C_STUSB4500" information (not certain what this is at the moment).
```{r}
data1 <- data1[(data1[,"name"] != "I2C_STUSB4500"),]
```

Only keep the "important" columns.
```{r}
cols <- c("type", "start_time", "duration", "address", "read", "data")
data1_sub1 <- data1[,cols]
#View(data1_sub1)
```

Now create subsets where the data comes from specific devices.
```{r}
address_type = data1_sub1[,"type"] == "address"
head(data1_sub1[address_type,])
```
Creating a function to convert hex data to ASCII (prints ASCII until it sees $0xFF$)
```{r}
convert_to_ascii <- function(data_vec)
{
  result <- c()
  for (data in data_vec) {
    hex <- as.hexmode(data)
    if (hex != 0xFF){
      ch <- rawToChar( as.raw( hex ) )
      result <- append(result,ch)
    }
  }
  return(result)
}

#vec <- c("0x3A","0x42","0xFF")

#convert_to_ascii(vec)
```


```{r}
data_type <- data1_sub1[,"type"] == "data"

d <- data1_sub1[data_type,"data"]
dat <- convert_to_ascii(d)


paste(dat,collapse = "")
```


